A tutorial of Bayesian beta regressions with brms in R

### 2024-12-08 code/01_data_checks.qmd
edit second case study

>>>>

## Vowel nasalisation

```{r}
#| label: read-nasal
nasal <- read_csv("https://raw.githubusercontent.com/ChristopherCarignan/journal-articles/refs/heads/master/rtMRI-velum/velum_data.csv") |> 
  filter(
    stress == "N",
    vowel %in% c("a_", "E_", "I_", "O_", "U_")
  ) |> 
  mutate(
    voicing = case_when(
      post %in% c("nt__", "nt_@", "nt_6", "nt_a") ~ "voiceless",
      post %in% c("nd_@", "nd_6", "nd_a") ~ "voiced"
    ),
    vowel = str_to_lower(vowel) |> str_remove("_")
  ) |> 
  # drop codas not included in the analysis
  drop_na(voicing) |> 
  mutate(
    nas_dur = (Vokal_off - velumopening_maxvel_on) * 1000,
    nas_prop = nas_dur / (Vokal_dur * 1000),
    NC = ifelse(voicing == "voiceless", "nt", "nd")
  ) |> 
  # drop observations with wrong fMRI tracking
  filter(nas_prop > 0, nas_prop < 1) |> 
  select(
    speaker, label, vowel, NC, voicing, nas_prop
  )

write_csv(nasal, "data/carignan2021/nasal.csv")
```

```{r}
nasal |> 
  ggplot(aes(nas_prop, fill = voicing)) +
  geom_density(alpha = 0.5)
```

```{r}
nasal |> 
  ggplot(aes(nas_prop, fill = voicing)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~vowel)
```

### 2024-12-08 manuscript/manuscript.qmd
add second case study
edit second case study

---
title: A tutorial of Bayesian beta regressions with brms in R
author:
  - name: Stefano Coretta
    email: s.coretta@ed.ac.uk
    affiliations: 
        - id: uoe
          name: University of Edinburgh
          department: Linguistics and English Language
          address: 3 George Sq
          city: Edinburgh
          state: United Kingdom
          postal-code: EH8 9AD
    attributes:
        corresponding: true
    note: This is the first author footnote.
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, ɔ, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess these patterns. ["expectations" XXX]

@@

We will use brms to fit Bayesian beta regressions. [XXX why Bayesian]. 
The model has voicing proportion as the outcome variable and the following terms: an interaction between vowel (/i, e, a, ɔ, u/) and second consonant C2 (/k, t, p/), centred speech rate (number of syllables per second); as varying (aka random) terms, by-speaker varying coefficients for the vowel/consonant interaction and for centred speech rate.^[Footnote about Gelman's terminology for random effects.] The categorical predictors vowel and C2 are coded using indexing rather than traditional R contrasts: in R, this corresponds to suppressing the model's intercept with the `0 +` syntax; using indexing instead of contrasts makes it easier to specify priors. For pedagogical simplicity, the model will use the default priors, but note that in real data analyses contexts, priors should be specified by the user. I refer the readers to XXX.

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. The full summary with an explanation of each part can be found in XXX. For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Bayesian CrIs indicate that at a certain probability levels the "true" estimate lies within that interval: so, for example, a 90% CrI [A, B] indicates that there is a 90% probability that the "true" estimate is between A and B. Different probability levels correspond to different levels of confidence: the higher the probability the higher the confidence (always conditional on data and model). Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence. We round all values to the nearest 2 digits for clarity.

@@

The coefficients of a beta regression are estimated on the log-odds scale, as in Bernoulli/binomial (aka logistic) regressions. From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds [$\beta$ = 0.8, SD = 0.06]. Log-odds can be converted to odd ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD (for a more detailed explanation, see XXX).

@@

Before being able to plot the predictions, it's important to get familiar with the so-called posterior draws. [Bayesian MCMC XXX]. Posterior draws can be conveniently obtained with the `as_draws_df()`. For the moment, we will extract only the draws of the constant regression coefficients (model variables starting with `b_`). To check which coefficients are available in a model, use `get_variables()` from the tidybayes package. `as_draws_df()` returns a tibble where each column contains the drawn values of a coefficient. The probability distribution of the drawn values of each coefficient is the posterior probability distribution of that coefficient. Note that, due to the indexing coding of vowel and C2, all coefficient except `b_speech_rate_c` are *predicted log-odds* for each vowel/C2 combination (the drawn values for `b_speech_rate_c` are drawn *differences* in log-odds for each unit increase of speech rate). The drawn values are in log-odds, but we can convert them to proportions with `plogis()` (we will do this when plotting below).

@@

Finally, the package marginaleffects has two other convenience functions that return CrIs of comparisons across predictor levels (`avg_comparisons()`) and CrIs of posterior predictions across predictor levels (`avg_predictions`). [XXX]

@@

# Case study 2: pre-nasalisation in Greek

>>>>

---
title: A tutorial of Bayesian beta regressions with brms in R
author:
  - name: Stefano Coretta
    email: s.coretta@ed.ac.uk
    affiliations: 
        - id: uoe
          name: University of Edinburgh
          department: Linguistics and English Language
          address: 3 George Sq
          city: Edinburgh
          state: United Kingdom
          postal-code: EH8 9AD
    attributes:
        corresponding: true
    note: This is the first author footnote.
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: linguistics.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: authoryear
---

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, ɔ, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess these patterns. \["expectations" XXX\]

@@

We will use brms to fit Bayesian beta regressions. \[XXX why Bayesian\]. The model has voicing proportion as the outcome variable and the following terms: an interaction between vowel (/i, e, a, ɔ, u/) and second consonant C2 (/k, t, p/), centred speech rate (number of syllables per second); as varying (aka random) terms, by-speaker varying coefficients for the vowel/consonant interaction and for centred speech rate.[^1] The categorical predictors vowel and C2 are coded using indexing rather than traditional R contrasts: in R, this corresponds to suppressing the model's intercept with the `0 +` syntax; using indexing instead of contrasts makes it easier to specify priors. For pedagogical simplicity, the model will use the default priors, but note that in real data analyses contexts, priors should be specified by the user. I refer the readers to XXX.

[^1]: Footnote about Gelman's terminology for random effects.

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. The full summary with an explanation of each part can be found in XXX. For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Bayesian CrIs indicate that at a certain probability levels the "true" estimate lies within that interval: so, for example, a 90% CrI \[A, B\] indicates that there is a 90% probability that the "true" estimate is between A and B. Different probability levels correspond to different levels of confidence: the higher the probability the higher the confidence (always conditional on data and model). Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence. We round all values to the nearest 2 digits for clarity.

@@

The coefficients of a beta regression are estimated on the log-odds scale, as in Bernoulli/binomial (aka logistic) regressions. From the summary, we see that speech rate (number of syllables per second) has a positive effect on voicing proportion: the 80% CrI is between 0.01 and 0.15 log-odds \[$\beta$ = 0.8, SD = 0.06\]. Log-odds can be converted to odd ratios by exponentiating the value: 0.01-0.15 log odds correspond to an odd ratio of 1.01 to 1.16, or as percentages, to an increase of voicing of 1 to 16% for every increase of one syllable per second. Since this is an 80% CrI, we can be 80% confident that the true effect of speech rate is between 1-16% increase of voicing proportion, conditional on the data and model. Note that transforming measures this way is appropriate *only* with quantile-based measures (like CrIs) but not with moments like the mean and standard deviation: to correctly get mean and SDs in the transformed scale, you must first extract the posterior draws (see below), convert them and then take moments such as mean and SD (for a more detailed explanation, see XXX).

@@

Before being able to plot the predictions, it's important to get familiar with the so-called posterior draws. \[Bayesian MCMC XXX\]. Posterior draws can be conveniently obtained with the `as_draws_df()`. For the moment, we will extract only the draws of the constant regression coefficients (model variables starting with `b_`). To check which coefficients are available in a model, use `get_variables()` from the tidybayes package. `as_draws_df()` returns a tibble where each column contains the drawn values of a coefficient. The probability distribution of the drawn values of each coefficient is the posterior probability distribution of that coefficient. Note that, due to the indexing coding of vowel and C2, all coefficient except `b_speech_rate_c` are *predicted log-odds* for each vowel/C2 combination (the drawn values for `b_speech_rate_c` are drawn *differences* in log-odds for each unit increase of speech rate). The drawn values are in log-odds, but we can convert them to proportions with `plogis()` (we will do this when plotting below).

@@

Finally, the package marginaleffects has two other convenience functions that return CrIs of comparisons across predictor levels (`avg_comparisons()`) and CrIs of posterior predictions across predictor levels (`avg_predictions`). \[XXX\]

@@

# Case study 2: coarticulatory vowel nasalisation

For the second case study we will use data from @carignan2021. The study looked at properties of nasality in German VNC sequences. Here, we will focus on the effect of C voicing (voiceless /t/ vs voiced /d/) on the proportion of nasalisation within the vowel in the VNC sequence. Previous work on coarticulatory nasalisation in English has suggested that vowels followed by an NC sequence where C is voiceless (NT) should show earlier coarticulatory nasalisation than vowels followed by an NC sequence where C is voiced [ND, see review in @carignan2021]. This pattern has been suggested to be driven by the articulatory and acoustic incompatibility of voicelessness and nasalisation, by which the velum opening gesture of the nasal consonant is pushed away (i.e. earlier) when the consonant following the nasal is voiceless. Everything else being equal, a greater proportion of vowel nasalisation (from the perspective of time) should be found in vowels followed by NT than in vowels followed by ND.

We will model the proportion of coarticulatory nasalisation in the German short vowels /i, e, a, o, u/ when followed by /nt/ or /nd/, using a Bayesian beta regression model. The proportion was calculated as the proportion of the nasal interval to the duration of the vowel. The nasal interval was defined thus: the interval between the time of peak velocity of velum opening to the offset of the vowel.

First, let's read and plot the data.

```{r}
#| label: nasal
nasal <- read_csv("data/carignan2021/nasal.csv")
nasal
```

-   `speaker` indicates the speaker ID.

-   `label` is the word label as given in the original data.

-   `vowel` is the target vowel in the VNC sequence.

-   `NC` is the NC sequence.

-   `voicing` indicates the voicing of C.

-   `nas_prop` is the proportion of coarticulatory nasalisation of the vowel.

```{r}
#| label: fig-nasal
#| fig-cap: "Proportion of coarticulatory nasalisation during the vowel in VNC sequences in German, depending on C voicing."
#| echo: false

nasal |> 
  ggplot(aes(vowel, nas_prop, colour = voicing)) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.2), alpha = 0.8) +
  scale_color_brewer(type = "qual") +
  labs(x = "Vowel", y = "Nasalisation proportion", colour = "C voicing")

```

@fig-nasal shows the proportion of coarticulatory nasalisation in vowels followed by /nd/ (voiced) vs /nt/ (voiceless) sequences, for the short vowels /i, e, a, o, u/. We can see a pattern of higher nasalisation proportion in vowels followed by /nt/, at least in the vowels /a, i, o/. For /e, u/, the distribution of nasalisation proportion seems to be similar between the voiced and voiceless contexts.

Now onto modelling with a beta regression. Note that a full appropriate model would include further predictors (both constant and varying), but for simplicity here we include only the following predictors: voicing (voiced /nd/ vs voiceless /nt/), vowel (/i, e, a, o, u/), including an interaction between them. As varying terms, we include a varying intercept by speaker and a by-speaker varying slope for voicing and vowel in interaction. As with the model from the first case study, voicing and vowel are coded using indexing, by suppressing the intercept with `0 +`. Here's the code of the model.

```{r}
#| label: nas-prop-bm

nas_prop_bm <- brm(
  nas_prop ~ 0 + voicing:vowel + (0 + voicing:vowel | speaker),
  data = nasal,
  family = Beta,
  cores = 4,
  seed = 3749,
  file = "data/cache/nas_prop_bm"
)
```

### 2024-12-08 manuscript/manuscript.tex
edit second case study

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

@@

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

@@

\includegraphics{manuscript_files/figure-pdf/fig-ita-egg-1.pdf}

@@

\includegraphics{manuscript_files/figure-pdf/fig-voi-prop-bm-1-1.pdf}

@@

\includegraphics{manuscript_files/figure-pdf/voi-prop-bm-draws-long-c2-1.pdf}

@@

\includegraphics{manuscript_files/figure-pdf/fig-diff-p-tk-1.pdf}

@@

\includegraphics{manuscript_files/figure-pdf/voi-prop-bm-cond-1.pdf}

@@

\renewcommand\refname{Case study 2: pre-nasalisation in Greek}
  \bibliography{bibliography.bib}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

@@

\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

@@

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-ita-egg-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-voi-prop-bm-1-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/voi-prop-bm-draws-long-c2-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-diff-p-tk-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/voi-prop-bm-cond-1.pdf}}

@@

\section{Case study 2: coarticulatory vowel
nasalisation}\label{case-study-2-coarticulatory-vowel-nasalisation}

For the second case study we will use data from \citet{carignan2021}.
The study looked at properties of nasality in German VNC sequences.
Here, we will focus on the effect of C voicing (voiceless /t/ vs voiced
/d/) on the proportion of nasalisation within the vowel in the VNC
sequence. Previous work on coarticulatory nasalisation in English has
suggested that vowels followed by an NC sequence where C is voiceless
should show earlier coarticulatory nasalisation than vowels followed by
an NC sequence where C is voiced \citep[see review in][]{carignan2021}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nasal }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"data/carignan2021/nasal.csv"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Rows: 643 Columns: 6
-- Column specification --------------------------------------------------------
Delimiter: ","
chr (5): speaker, label, vowel, post, voicing
dbl (1): nas_prop

i Use `spec()` to retrieve the full column specification for this data.
i Specify the column types or set `show_col_types = FALSE` to quiet this message.
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{nas\_prop\_bm }\OtherTok{\textless{}{-}} \FunctionTok{brm}\NormalTok{(}
\NormalTok{  nas\_prop }\SpecialCharTok{\textasciitilde{}} \DecValTok{0} \SpecialCharTok{+}\NormalTok{ voicing}\SpecialCharTok{:}\NormalTok{vowel }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{0} \SpecialCharTok{+}\NormalTok{ voicing}\SpecialCharTok{:}\NormalTok{vowel }\SpecialCharTok{|}\NormalTok{ speaker),}
  \AttributeTok{data =}\NormalTok{ nasal,}
  \AttributeTok{family =}\NormalTok{ Beta,}
  \AttributeTok{cores =} \DecValTok{4}\NormalTok{,}
  \AttributeTok{seed =} \DecValTok{3749}\NormalTok{,}
  \AttributeTok{file =} \StringTok{"data/cache/nas\_prop\_bm"}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(nas\_prop\_bm, }\AttributeTok{prob =} \FloatTok{0.8}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
 Family: beta 
  Links: mu = logit; phi = identity 
Formula: nas_prop ~ 0 + voicing:vowel + (0 + voicing:vowel | speaker) 
   Data: nasal (Number of observations: 643) 
  Draws: 4 chains, each with iter = 2000; warmup = 1000; thin = 1;
         total post-warmup draws = 4000

Multilevel Hyperparameters:
~speaker (Number of levels: 35) 
                                                       Estimate Est.Error
sd(voicingvoiced:vowela_)                                  0.45      0.13
sd(voicingvoiceless:vowela_)                               0.37      0.10
sd(voicingvoiced:vowelE_)                                  0.56      0.18
sd(voicingvoiceless:vowelE_)                               0.34      0.13
sd(voicingvoiced:vowelI_)                                  0.71      0.18
sd(voicingvoiceless:vowelI_)                               0.83      0.16
sd(voicingvoiced:vowelO_)                                  0.36      0.22
sd(voicingvoiceless:vowelO_)                               0.24      0.18
cor(voicingvoiced:vowela,_voicingvoiceless:vowela_)        0.49      0.22
cor(voicingvoiced:vowela,_voicingvoiced:vowelE_)           0.29      0.25
cor(voicingvoiceless:vowela,_voicingvoiced:vowelE_)        0.16      0.25
cor(voicingvoiced:vowela,_voicingvoiceless:vowelE_)        0.25      0.27
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelE_)     0.42      0.25
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelE_)        0.17      0.28
cor(voicingvoiced:vowela,_voicingvoiced:vowelI_)           0.15      0.26
cor(voicingvoiceless:vowela,_voicingvoiced:vowelI_)        0.17      0.26
cor(voicingvoiced:vowelE,_voicingvoiced:vowelI_)           0.23      0.26
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelI_)        0.29      0.27
cor(voicingvoiced:vowela,_voicingvoiceless:vowelI_)       -0.11      0.24
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelI_)     0.16      0.23
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelI_)        0.14      0.25
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelI_)     0.33      0.25
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelI_)        0.34      0.23
cor(voicingvoiced:vowela,_voicingvoiced:vowelO_)           0.20      0.31
cor(voicingvoiceless:vowela,_voicingvoiced:vowelO_)        0.13      0.31
cor(voicingvoiced:vowelE,_voicingvoiced:vowelO_)           0.10      0.31
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelO_)        0.07      0.31
cor(voicingvoiced:vowelI,_voicingvoiced:vowelO_)           0.14      0.31
cor(voicingvoiceless:vowelI,_voicingvoiced:vowelO_)       -0.06      0.29
cor(voicingvoiced:vowela,_voicingvoiceless:vowelO_)        0.03      0.32
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelO_)    -0.05      0.32
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelO_)        0.09      0.32
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelO_)     0.03      0.33
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelO_)        0.12      0.32
cor(voicingvoiceless:vowelI,_voicingvoiceless:vowelO_)     0.03      0.31
cor(voicingvoiced:vowelO,_voicingvoiceless:vowelO_)        0.08      0.33
                                                       l-80% CI u-80% CI Rhat
sd(voicingvoiced:vowela_)                                  0.29     0.62 1.00
sd(voicingvoiceless:vowela_)                               0.25     0.50 1.00
sd(voicingvoiced:vowelE_)                                  0.33     0.79 1.00
sd(voicingvoiceless:vowelE_)                               0.18     0.50 1.00
sd(voicingvoiced:vowelI_)                                  0.50     0.96 1.00
sd(voicingvoiceless:vowelI_)                               0.64     1.04 1.00
sd(voicingvoiced:vowelO_)                                  0.08     0.66 1.00
sd(voicingvoiceless:vowelO_)                               0.04     0.49 1.00
cor(voicingvoiced:vowela,_voicingvoiceless:vowela_)        0.20     0.76 1.00
cor(voicingvoiced:vowela,_voicingvoiced:vowelE_)          -0.05     0.60 1.00
cor(voicingvoiceless:vowela,_voicingvoiced:vowelE_)       -0.17     0.50 1.00
cor(voicingvoiced:vowela,_voicingvoiceless:vowelE_)       -0.10     0.59 1.00
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelE_)     0.09     0.72 1.00
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelE_)       -0.22     0.53 1.00
cor(voicingvoiced:vowela,_voicingvoiced:vowelI_)          -0.20     0.49 1.00
cor(voicingvoiceless:vowela,_voicingvoiced:vowelI_)       -0.18     0.50 1.00
cor(voicingvoiced:vowelE,_voicingvoiced:vowelI_)          -0.11     0.56 1.00
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelI_)       -0.07     0.62 1.00
cor(voicingvoiced:vowela,_voicingvoiceless:vowelI_)       -0.42     0.20 1.00
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelI_)    -0.13     0.46 1.00
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelI_)       -0.19     0.44 1.00
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelI_)     0.00     0.63 1.00
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelI_)        0.03     0.62 1.00
cor(voicingvoiced:vowela,_voicingvoiced:vowelO_)          -0.22     0.59 1.00
cor(voicingvoiceless:vowela,_voicingvoiced:vowelO_)       -0.27     0.53 1.00
cor(voicingvoiced:vowelE,_voicingvoiced:vowelO_)          -0.33     0.50 1.00
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelO_)       -0.34     0.47 1.00
cor(voicingvoiced:vowelI,_voicingvoiced:vowelO_)          -0.27     0.52 1.00
cor(voicingvoiceless:vowelI,_voicingvoiced:vowelO_)       -0.44     0.33 1.00
cor(voicingvoiced:vowela,_voicingvoiceless:vowelO_)       -0.40     0.45 1.00
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelO_)    -0.46     0.37 1.00
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelO_)       -0.34     0.51 1.00
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelO_)    -0.41     0.46 1.00
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelO_)       -0.32     0.54 1.00
cor(voicingvoiceless:vowelI,_voicingvoiceless:vowelO_)    -0.39     0.43 1.00
cor(voicingvoiced:vowelO,_voicingvoiceless:vowelO_)       -0.37     0.50 1.00
                                                       Bulk_ESS Tail_ESS
sd(voicingvoiced:vowela_)                                  1686     1641
sd(voicingvoiceless:vowela_)                               2099     2574
sd(voicingvoiced:vowelE_)                                  1536     1551
sd(voicingvoiceless:vowelE_)                               2319     1734
sd(voicingvoiced:vowelI_)                                  2498     3094
sd(voicingvoiceless:vowelI_)                               3333     3115
sd(voicingvoiced:vowelO_)                                  1620     1698
sd(voicingvoiceless:vowelO_)                               2295     2196
cor(voicingvoiced:vowela,_voicingvoiceless:vowela_)        2144     2507
cor(voicingvoiced:vowela,_voicingvoiced:vowelE_)           2466     2751
cor(voicingvoiceless:vowela,_voicingvoiced:vowelE_)        2821     3574
cor(voicingvoiced:vowela,_voicingvoiceless:vowelE_)        3289     3353
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelE_)     3534     3625
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelE_)        4027     3622
cor(voicingvoiced:vowela,_voicingvoiced:vowelI_)           2057     2599
cor(voicingvoiceless:vowela,_voicingvoiced:vowelI_)        2350     2928
cor(voicingvoiced:vowelE,_voicingvoiced:vowelI_)           2143     2832
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelI_)        1964     3115
cor(voicingvoiced:vowela,_voicingvoiceless:vowelI_)        1792     2459
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelI_)     2219     2880
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelI_)        2232     2731
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelI_)     1602     2249
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelI_)        2271     3182
cor(voicingvoiced:vowela,_voicingvoiced:vowelO_)           3973     3016
cor(voicingvoiceless:vowela,_voicingvoiced:vowelO_)        5614     3512
cor(voicingvoiced:vowelE,_voicingvoiced:vowelO_)           4179     3070
cor(voicingvoiceless:vowelE,_voicingvoiced:vowelO_)        4760     3338
cor(voicingvoiced:vowelI,_voicingvoiced:vowelO_)           4135     3265
cor(voicingvoiceless:vowelI,_voicingvoiced:vowelO_)        4320     3583
cor(voicingvoiced:vowela,_voicingvoiceless:vowelO_)        7265     3088
cor(voicingvoiceless:vowela,_voicingvoiceless:vowelO_)     5934     3240
cor(voicingvoiced:vowelE,_voicingvoiceless:vowelO_)        6140     3465
cor(voicingvoiceless:vowelE,_voicingvoiceless:vowelO_)     5229     3304
cor(voicingvoiced:vowelI,_voicingvoiceless:vowelO_)        4597     3612
cor(voicingvoiceless:vowelI,_voicingvoiceless:vowelO_)     6014     3479
cor(voicingvoiced:vowelO,_voicingvoiceless:vowelO_)        3033     3351

Regression Coefficients:
                         Estimate Est.Error l-80% CI u-80% CI Rhat Bulk_ESS
voicingvoiced:vowela_       -0.61      0.12    -0.76    -0.45 1.00     3695
voicingvoiceless:vowela_    -0.07      0.09    -0.19     0.04 1.00     3582
voicingvoiced:vowelE_       -0.19      0.15    -0.38     0.01 1.00     3940
voicingvoiceless:vowelE_    -0.25      0.10    -0.38    -0.12 1.00     5156
voicingvoiced:vowelI_       -0.74      0.19    -0.98    -0.51 1.00     4090
voicingvoiceless:vowelI_    -0.12      0.17    -0.33     0.10 1.00     4077
voicingvoiced:vowelO_       -0.33      0.16    -0.54    -0.13 1.00     6095
voicingvoiceless:vowelO_     0.25      0.16     0.05     0.45 1.00     6834
                         Tail_ESS
voicingvoiced:vowela_        3160
voicingvoiceless:vowela_     3300
voicingvoiced:vowelE_        2601
voicingvoiceless:vowelE_     3268
voicingvoiced:vowelI_        3357
voicingvoiceless:vowelI_     3305
voicingvoiced:vowelO_        2719
voicingvoiceless:vowelO_     2927

Further Distributional Parameters:
    Estimate Est.Error l-80% CI u-80% CI Rhat Bulk_ESS Tail_ESS
phi     4.73      0.30     4.35     5.12 1.00     2477     3192

Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
and Tail_ESS are effective sample size measures, and Rhat is the potential
scale reduction factor on split chains (at convergence, Rhat = 1).
\end{verbatim}

  \bibliography{linguistics.bib}
